\mytitle

### 2023-05-08 chapters/depsynth/impl.tex
Depsynth extension first parts

\section{Implementation}\label{s:impl}

@@

>>>>

\section{Optimizations and Design Choices}\label{s:impl}

@@

\paragraph{Attempting graph search with a \tord solver.}
One bottleneck in the time \depsynth takes to find a complete set of
dependency rules comes from the time it takes to search for a minimal
happens-before graph for a given litmus test.
This section explores a strategy that we explored to limit this bottleneck.
Specifically, we encode the happens-before graph search problem
in the theory of ordering consistency (\tord)\todo{cite}
and execute the search with an existing \tord solver.
Ultimately, we found that this different search strategy did not 
improve the overall runtime, but we find this negative
result worth reporting.

% TODO elaborate on \tord

% TODO present results
Intuitively, % TODO discuss why this didn't work

\subsection{Faster Consistency Checks for Litmus Tests}
\label{s:improved-search}
As \cref{sec:eval:shardstore} discusses,
a large majority of the litmus tests seen during the \depsynth
algorithm do not result in new dependency rules
(\depsynth generated new rules for only \shardstoretestsused of \shardstoreinputtests
 litmus tests seen for \shardstore).
However, for each litmus test in the input set, \depsynth
must perform a check that the accumulated dependency rules
guarantee the crash consistency of the test.
For synthesizing rules in \shardstore,
these take up \shardstoreverificationminutes minutes (\shardstoreverificationpercent\%)
of the overall search time.

\paragraph{Decomposing crash consistency queries.}
As \cref{todo} explains, \depsynth offloads a query to an SMT
solver when it first encounters a new litmus test to determine
whether or not the current set of dependency rules satisfy the
crash consistency property for that test.
In practice, this query is encoded by representing the \textit{committed status}
of each write from a litmus test as a boolean variable
and each edge in the happens-before graph as an implication between those variables.
% The value of these variables also affects the disk state,
% which is used
For tests that generate a large happens-before graph
with respect to the current dependency rules,
the query can take tens of seconds.

Experimentally, we observed that for these queries with long runtimes,
decomposing the query by concretizing one write-committed variable
drastically speeds up overall solving time
(at most \splitvariablebestspeedup \times speedup for a single litmus test).
Specifically, considering the set of write-committed variables $V$,
the happens-before graph $G\subset V\times V$,
and the original encoding for the litmus test crash consistency check $P(G)$,
we choose a variable $v_0\in V$ and issue the following two queries:
\begin{enumerate}
  \item $v_0 \wedge \forall v\in V. (v, v_0)\in G \rightarrow v) \wedge P(G)$
  \item $\neg v_0 \wedge \forall v\in V. (v, v_0)\in G \rightarrow \neg v) \wedge P(G)$
\end{enumerate}
The litmus test is crash consistent with respect to the dependency rules
if and only if both queries succeed.

Intuitively, this decomposition can result in faster solving times for two reasons.
First, this optimization can be seen as a pre-processing variable selection step.
By taking advantage of the relationship between nodes in the happens-before graph
(which is abstracted away in the constraints sent to the solver),
we are effectively telling the solver to select a good first variable for branching.
Second, concretizing write-committed variables can also indirectly simplify the
crash consistency predicate for the litmus test.
The crash consistency predicate is a function over disk states,
and the disk state itself depends on the write-committed variables.
Thus, by assigning concrete values to some of those variables,
constraints representing the crash consistency predicate over the disk state
may be simplified or eliminated.

\paragraph{Concretizing More Variables.}
%Specifically, we choose a variable whose corresponding 
Upon further experimentation, we noticed both that the number of
concretized variables and the specific variables chosen for concretization
significantly impacted solving time.
Ultimately, % TODO chose log n vars such that the most edges were eliminated

### 2023-05-08 chapters/depsynth/results.tex
Depsynth extension first parts

\subsection{Other Storage Systems}\label{sec:eval:other}

In addition to the \shardstore case study, % in \cref{sec:eval:shardstore},
we have also used \depsynth
to implement a log-structured file system~\cite{rosenblum:lfs}.
%with support for files and directories.
The file system supports five standard POSIX operations:
\texttt{open}, \texttt{creat}, \texttt{write}, \texttt{close}, and \texttt{mkdir}.
While our implementation is simple (300 lines of Racket code) compared to production file systems,
it has metadata structures for files and directories,
and so has its own subtle crash consistency requirements.
For example, updates to data and inode blocks must reach the
disk before the pointer to the tail of the log is updated.
To synthesize dependency rules for this file system,
we randomly generated \lfsinputtests{} litmus tests
with at most \lfsmaxops{} operations.
\depsynth synthesized a set of \lfsnumrules{} dependency rules
in \lfssynthesistime{} to make the file system crash consistent,
and during the search,
invokes \textsc{RulesForTest} for only \lfstestsused{} tests.
This result shows that \depsynth can automate crash consistency for storage systems other than key-value stores.

>>>>

\subsection{Other Case Studies}\label{sec:eval:other}
In addition to the \shardstore case study, % in \cref{sec:eval:shardstore},
we have applied \depsynth to two other storage systems.
The first is a modification of \shardstore that relaxes assumptions made on the underlying disk hardware.
The second is a simple log-strucutred file system.
\depsynth was effectively able to synthesize rules for both of these
additional cases, demonstrating the generality of our approach.

\paragraph{Log-Structured File System.}
In addition to the \shardstore case study, % in \cref{sec:eval:shardstore},
we have also used \depsynth
to implement a log-structured file system~\cite{rosenblum:lfs}.
%with support for files and directories.
The file system supports five standard POSIX operations:
\texttt{open}, \texttt{creat}, \texttt{write}, \texttt{close}, and \texttt{mkdir}.
While our implementation is simple (300 lines of Racket code) compared to production file systems,
it has metadata structures for files and directories,
and so has its own subtle crash consistency requirements.
For example, updates to data and inode blocks must reach the
disk before the pointer to the tail of the log is updated.
To synthesize dependency rules for this file system,
we randomly generated \lfsinputtests{} litmus tests
with at most \lfsmaxops{} operations.
\depsynth synthesized a set of \lfsnumrules{} dependency rules
in \lfssynthesistime{} to make the file system crash consistent,
and during the search,
invokes \textsc{RulesForTest} for only \lfstestsused{} tests.
This result shows that \depsynth can automate crash consistency for storage systems other than key-value stores.
